Secure Composition of Robust and Optimising Compilers

### 2023-07-09 popl/main.tex
make use of -> use

This section defines programming languages that the secure compilers defined in the next section will make use of\MP{make use of -> use! 3 words when 1 is sufficient}.
To this end, this section defines the languages $\Ltms$, $\Ltrg$, $\Lms$, and $\Lscct$ which share many common elements (presented in \Cref{subsec:cs:defs}).
In this paper, $\Ltms$ is the only statically typed language and exhibits the property that all well-typed programs are \gls{tms} (\Cref{??}).
However, not all $\Ltms$ programs are \gls{sms}.\MP{reworded. was imprecise}
That is, there are well--typed $\Ltms$ programs that perform an out--of--bounds access.
In contrast, $\Ltrg$ is untyped and does not provide any guarantees with regards to \gls{ms} (\Cref{??}).
$\Lms$ is exactly the same language as $\Ltrg$, but this paper still distinguishes the two for sake of readability (\Cref{??}).
All three languages --- so $\Ltms$, $\Ltrg$, and $\Lms$ --- assume \gls{cct} to hold.

@@

It is now possible to make use of \Cref{thm:rtp} to extract a compiler from $\Ltms$ to $\Lms$ that is \gls{ms} by applying \Cref{thm:cca:rtp:tms,thm:ccb:rtp:sms}.
\MP{
	bad sentence. rewrite.
}

>>>>

This section defines programming languages that the secure compilers defined in the next section will use.
To this end, this section defines the languages $\Ltms$, $\Ltrg$, $\Lms$, and $\Lscct$ which share many common elements (presented in \Cref{subsec:cs:defs}).
In this paper, $\Ltms$ is the only statically typed language and exhibits the property that all well-typed programs are \gls{tms} (\Cref{??}).
However, not all $\Ltms$ programs are \gls{sms}.\MP{reworded. was imprecise}
That is, there are well--typed $\Ltms$ programs that perform an out--of--bounds access.
In contrast, $\Ltrg$ is untyped and does not provide any guarantees with regards to \gls{ms} (\Cref{??}).
$\Lms$ is exactly the same language as $\Ltrg$, but this paper still distinguishes the two for sake of readability (\Cref{??}).
All three languages --- so $\Ltms$, $\Ltrg$, and $\Lms$ --- assume \gls{cct} to hold.

@@

It is now possible to use \Cref{thm:rtp} to extract a compiler from $\Ltms$ to $\Lms$ that is \gls{ms} by applying \Cref{thm:cca:rtp:tms,thm:ccb:rtp:sms}.
\MP{
	bad sentence. rewrite.
}
